Finite Property Convex Elicitation Notes

### 2018-09-29 jessie-writeup/jessie-writeup.tex
Showing full dimensional level sets of trim

\begin{definition}
Let $\Gamma$ be a labeled property.
Define $\text{strip}(\Gamma) := \{ \Gamma_r : r \in \R \}$.
Informally, strip removes labels from the property.
\jessie{Strip includes the boundaries of level sets / lower dimensional level sets.}
\end{definition}

@@

\begin{conjecture}\label{conj:gam-prime-exists}
	Let $\Gamma$ be a nondegenerate elicitable property \jessie{with a finite set of level sets.}
	There exists a nondegenerate, nonredundant property $\Gamma'$ such that $\Gamma' \leq \Gamma$ and $\trim(\Gamma) = \strip(\Gamma')$.  
\end{conjecture}
\begin{proof}
\emph{Assumptions used: Finite level sets.}

@@

\begin{conjecture}\label{conj:trim-full-dim}
	Every level set of $\Theta := \trim(\Gamma)$ is full-dimensional  
\end{conjecture}

@@

	In order to understand $\trim(\Gamma)$ is, we use the $\Gamma' \leq \Gamma$ constructed in Conjecture~\ref{conj:gam-prime-exists}, and let $\R'$ be the set such that $\Gamma' = \Gamma\cap \R'$.
	First, we see $\Theta = \strip(\Gamma')$ is nonredundant in the unlabeled sense as $\Gamma'$ is nonredundant in the labeled set from Conjecture~\ref{conj:nonredundant-defs-equivalent}, since we know $\Gamma'$ is nonredundant-- and well-defined from Conjecture~\ref{conj:gam-prime-exists}.
	\jessie{To show.}

@@

	We proceed in 2 cases for a level set $\theta \in \Theta$:
	\begin{enumerate}
		\item For all $\theta' \in \Theta$, $\theta \cap \theta' = \emptyset$.
		We know the level set $\theta$ is closed by Lemma~\ref{lem:closed-level-sets}
		By definition of $\R'$, there is some $p \in \inter{\theta}$ so that for $r_\theta = \Gamma'(p)$, there is a ball $B(\epsilon, p)$ centered around $p$ so that for every $q \in B(\epsilon, p)$, $r_\theta \in \Gamma'(q)$.
%		(In fact, as $\Theta$ is nonredundant, we claim $r_\theta = \Gamma'(q)$. \jessie{Need to show?})
		Therefore, the level set $\Gamma_{r_\theta} = \theta$ is full dimensional as it has nonempty interior.

@@

		By nonredundancy of $\Gamma'$, we then observe nonredundancy of $\Theta$, we know that $\mu(\theta \cap \theta') = 0$.
		We want to show that $\theta$ is full dimensional.
		\jessie{TODO}

@@

\begin{conjecture}\label{conj:nonredundant-defs-equivalent}
	An elicitable property with finite level sets $\Gamma$ is nonredundant (in the labeled definition) $\iff$ $\strip(\Gamma)$ is nonredundant (in the unlabeled definition.)
\end{conjecture}
\begin{proof}
	We show both directions.\\
	\begin{enumerate}
		\item [$\implies$]
		Let the property $\Gamma:\P \to \R$ be nonredundant.
		Then for any two reports $r, r' \in \R$ with $r \neq r'$, the level sets $\theta := \Gamma_r \not \subseteq \Gamma_{r'}$ and $\theta' := \Gamma_{r'} \not \subseteq \Gamma_r$.
		In what follows, $G : \P \to \R$ is the Bayes Risk, or optimal report given a distribution $p$.
		Each report $r$ corresponds to a labeling of the subgradient sets of $G$.

@@

		\item[$\impliedby$] 
		Say that for any two full dimensional level sets $\theta, \theta' \in \Theta := \strip(\Gamma)$ that $\mu(\theta \cap \theta') = 0$.
		Then there are reports $r, r' \in \R$ such that $\theta = \Gamma_r$ and $\theta' = \Gamma_{r'}$.
		As $\mu(\Gamma_r \cap \Gamma_{r'}) = 0 \implies$ the interior of $\Gamma_r \cap \Gamma_{r'}$ is empty.
		Therefore, the intersection of the two level sets is not full dimensional.

@@

Therefore if the function $\trim(\Gamma)$ is well-defined and finite, then the labeled property $\Gamma$ has a finite set of full-dimensional level sets and for every $\theta \in \Theta$, there is a unique optimal report for every distribution $p \in \inter{\theta}$.

@@

look at Rockefellar- algebraic interior
Appendix of complexity paper- the Bayes Risk must be strictly concave.

Order of To-Dos -- ordered by dependency
\begin{enumerate}
\item Show there exists a nondeg, nonred $\Gamma' \leq \Gamma$ that $\trim(\Gamma) = \strip(\Gamma')$. (Conjecture~\ref{conj:gam-prime-exists}) -- Done
\item Show every level set of the trim is Full Dimensional (Conjecture~\ref{conj:trim-full-dim}).
\item Proof of $2 \implies 1$-- Done-ish.
\end{enumerate}

>>>>

\begin{definition}
Let $\Gamma$ be a labeled property.
Define $\text{strip}(\Gamma) := \{ \Gamma_r : r \in \R \}$.
Informally, strip removes labels from the property.
\jessie{Note: Strip includes the boundaries of level sets / lower dimensional level sets.}
\end{definition}

@@

\begin{conjecture}\label{conj:gam-prime-exists}
	Let $\Gamma$ be a nondegenerate elicitable property with a finite set of level sets.
	There exists a nondegenerate, nonredundant property $\Gamma'$ such that $\Gamma' \leq \Gamma$ and $\trim(\Gamma) = \strip(\Gamma')$. \jessie{To be defined, but this should be moved after the definition of trim later anyways...} 
\end{conjecture}
\begin{proof}
\emph{Assumptions used: Finite level sets.}

@@

\begin{conjecture}\label{conj:trim-full-dim}
	Consider an elicitable property $\Gamma$ with finitely many level sets.
	Every $\theta \in \Theta := \trim(\Gamma)$ is full-dimensional  
\end{conjecture}

@@

	In order to understand what $\trim(\Gamma)$ is, we use the $\Gamma' \leq \Gamma$ constructed in Conjecture~\ref{conj:gam-prime-exists}, and let $\R'$ be the set such that $\Gamma' = \Gamma\cap \R'$.
	First, we see $\Theta = \strip(\Gamma')$ is nonredundant in the unlabeled definition (Definition~\ref{def:unlabeled-nonredundant}) as $\Gamma'$ is nonredundant in the labeled set from Conjecture~\ref{conj:nonredundant-defs-equivalent}, since we know $\Gamma'$ is nonredundant-- and well-defined from Conjecture~\ref{conj:gam-prime-exists}.

@@

	We proceed in 2 cases for a level set $\theta \in \Theta$:
	\begin{enumerate}
		\item For all $\theta' \in \Theta$, $\theta \cap \theta' = \emptyset$.
		\jessie{Doesn't this only happen when $\{\theta\} = \Theta$?}

		We know the level set $\theta$ is closed by Lemma~\ref{lem:closed-level-sets}.
		By definition of $\R'$, for $p \in \inter{\theta}$ so that for $r_\theta = \Gamma'(p)$, there is a ball $B(\epsilon, p)$ centered around $p$ so that for every $q \in B(\epsilon, p)$, $r_\theta \in \Gamma'(q)$.
%		(In fact, as $\Theta$ is nonredundant, we claim $r_\theta = \Gamma'(q)$. \jessie{Need to show?})
		Therefore, the level set $\Gamma_{r_\theta} = \theta$ is full dimensional as it has nonempty interior.

@@

		By nonredundancy of $\Gamma'$, we then observe nonredundancy of $\Theta$, we know that $\mu(\theta \cap \theta') = 0$.
		We want to show that $\theta$ is full dimensional.

		For contradiction, suppose $\theta \in \trim(\Gamma)$ is not full dimensional.
		By Conjecture~\ref{conj:gam-prime-exists}, there exists a nonredundant, nondegenerate $\Gamma' \leq \Gamma$ so that $\trim(\Gamma) = \strip(\Gamma')$.
		Consider $\R'$ so that $\Gamma' = \Gamma \cap \R'$ as constructed in the proof of Conjecture~\ref{conj:gam-prime-exists}.

		Suppose $\theta \in \trim(\Gamma)$ is not full dimensional.
		Then $\inter{\theta} = \emptyset$.
		As $\trim(\Gamma) = \strip(\Gamma')$, we observe that there is a unique $r \in \R'$ so that $\Gamma'_r = \theta$.
		However, $\inter{\theta} = \inter{\Gamma'_r} = \emptyset \implies r \not \in \R'$ by the construction of $\R'$.
		Since $\trim(\Gamma) = \strip(\Gamma')$ \emph{for all} nonredundant, nondegenerate $\Gamma' \leq \Gamma$-- including the $\Gamma'$ constructed in the proof of Conjecture~\ref{conj:gam-prime-exists}, then we conclude $\Gamma_r = \theta \not \in \strip(\Gamma') = \trim(\Gamma)$.

@@

\begin{conjecture}\label{conj:nonredundant-defs-equivalent}
	An elicitable property $\Gamma$ with finite level sets is nonredundant (in the labeled definition) $\iff$ $\strip(\Gamma)$ is nonredundant (in the unlabeled definition.)
\end{conjecture}
\begin{proof}
	We show both directions.\\
	\begin{enumerate}
		\item [$\implies$]
		Let the property $\Gamma:\P \to \R$ be nonredundant.
		Then for any two reports $r, r' \in \R$ with $r \neq r'$, the level sets $\theta := \Gamma_r \not \subseteq \Gamma_{r'}$ and $\theta' := \Gamma_{r'} \not \subseteq \Gamma_r$.
		In what follows, $G : \P \to \R$ is the Bayes Risk, or optimal report given a distribution $p$.
		Each report $r$ corresponds to a labeling of the subgradient sets of $G$.

@@

		\item[$\impliedby$] 
		Say that for any two full dimensional level sets $\theta, \theta' \in \Theta := \strip(\Gamma)$ that $\mu(\theta \cap \theta') = 0$.
		Then there are reports $r, r' \in \R$ such that $\theta = \Gamma_r$ and $\theta' = \Gamma_{r'}$.
		Since the property $\Gamma$ is elicitable, the level sets $\Gamma_r$ and $\Gamma_{r'}$ are convex.
		$\mu(\Gamma_r \cap \Gamma_{r'}) = 0 \implies$ the interior of $\Gamma_r \cap \Gamma_{r'}$ is empty.
		\jessie{Not necessarily... need to specify why convexity of level sets makes that true.
		All we know from the implication is that the interior has measure 0.}
		Therefore, the intersection of the two level sets is not full dimensional.

@@

Therefore if the function $\trim(\Gamma)$ is well-defined and finite, then the labeled property $\Gamma$ has a finite set of full-dimensional level sets and for every $\theta \in \Theta$, there is a unique optimal report for every distribution $p \in \inter{\theta}$.
\jessie{Uniqueness actually follows from concavity of Bayes Risk, since the measure of the sets with multiple viable labels has to be of measure zero, and can't be full dimensional.}

@@

\begin{enumerate}
\item[a.] look at Rockefellar- algebraic interior

\item[b.] Appendix of complexity paper- the Bayes Risk must be strictly concave.
\end{enumerate}

Order of To-Dos -- ordered by dependency
\begin{enumerate}
\item Show there exists a nondeg, nonred $\Gamma' \leq \Gamma$ that $\trim(\Gamma) = \strip(\Gamma')$. (Conjecture~\ref{conj:gam-prime-exists}) 
\item Show every level set of the trim is Full Dimensional (Conjecture~\ref{conj:trim-full-dim}).
\item Proof of $2 \implies 1$
\end{enumerate}
